### 2019-08-16 thesis.tex
*** empty log message ***

\subsection{The solar corona}
\label{sec:corona}
The source of the tenuous magnetized plasma permeating the heliosphere, and
also the origin of solar particles and radiation that may cause disruptive
space weather around Earth, is the outermost layer of the Sun: the solar
corona \cite{Cranmer2017,Klein2017}. The solar corona can be easily recognized
as the bright halo that appears around the hidden Sun during solar eclipses.
\autoref{corona} shows two beautiful photographs of the corona, taken in two
different solar eclipses, August 21 $2017$ and $2019$. In both pictures, one
can see the moon covering the bright photosphere, allowing us to have a
glimpse of the thin, but ultra-hot coronal plasma. Non-intuitively, the solar
corona is, at the same time, the thinnest and the hottest outer layer of
the Sun, where the temperature is of the order of $10^6\unit{K}$.

\begin{figure}[hb]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{corona2017.png}
    \includegraphics[width=0.892\textwidth]{corona2019.png}
    \caption{Solar corona captured during the total solar eclipse of 2017 (top panel)
      and 2019 (lower panel). The reddish contour at some regions is the chromosphere,
      and the reddish arcs are solar prominences, chromospheric plasma structures that
      penetrate the coronal region \cite{BenzA2002,Habbal2010,JeanVlaude2015}.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 15/08/2019}.}
    \label{corona}
  \end{center}
\end{figure}

>>>>

\subsection{The solar corona}
\label{sec:corona}
The source of the tenuous magnetized plasma permeating the heliosphere, and
also the origin of solar particles and radiation that may cause disruptive
space weather around Earth, is the outermost layer of the Sun: the solar
corona \cite{Cranmer2017,Klein2017}. The solar corona can be easily recognized
as the bright halo that appears around the hidden Sun during solar eclipses.
\autoref{corona} shows two beautiful photographs of the corona, taken in two
different solar eclipses, August 21 $2017$ and July 2 $2019$. In both pictures,
one can see the moon covering the bright photosphere, allowing us to have a
glimpse of the thin, but ultra-hot coronal plasma.

Counter-intuitively, the solar corona is, at the same time, the most tenuous
and the hottest outer layer of the Sun. At the top of the chromosphere, where
the temperature might reach $20,000\,\unit{K}$, in a relatively narrow interface,
the \emph{solar transition region}, the plasma temperature rises abruptly to
$\sim 10^6\,\unit{K}$ \cite{BenzA2002}. It has been almost eighty years since
the extreme coronal temperature came as the only reasonable explanation for the
origin of the spectral lines observed in the solar corona \cite{Hunter1942},
in a classical case of an answer that brings a more troublesome question. 
Since then, several mechanisms have been proposed \cite{Parker1988,Scudder92b,
  Vinas2000,PP14}, not only to comprehend the heating of the solar corona,
but also the acceleration of the solar wind. Another unsolved problem that is
directly connected to the inverted temperature profile of the solar corona, is
regarding where and how the non-Maxwellian velocity distribution functions with
suprathermal tails, observed in the solar wind, are formed.

In \cite{Tigik2017a} ...
present a new fundamental mechanism that is capable
the formation of suprathermal tails in the electron velocity distribution function

proposing a fundamental mechanism,
the electrostatic bremsstrahlung, that might take electrons out of the thermal
equilibrium

\begin{figure}[hb]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{corona2017.png}
    \includegraphics[width=0.892\textwidth]{corona2019.png}
    \caption{Solar corona captured during the total solar eclipse of 2017 (top panel)
      and 2019 (lower panel). The reddish contour at some regions is the chromosphere,
      and the reddish arcs are solar prominences, chromospheric plasma structures that
      penetrate the coronal region.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 15/08/2019}.}
    \label{corona}
  \end{center}
\end{figure}
